---
title: "Pitch for app"
author: "Amandine Ligot"
date: "3 december 2018"
output: ioslides_presentation
---


## Motivation

As a chemist it is sometime important to know about the relationship between the vapor pressure of Mercury (in mm) and the temperature
This app enables the user to choose a model in order to fit the evolution of pressure in function of temperature.

## Data

The data can be loaded from the Pressure dataset. It contains 19 rows.

```{r}
head(pressure)
```

## The data in image

```{r}
plot(pressure$temperature, pressure$pressure, 
     xlab = "Temperature in degC", ylab = "Pressure (in mm)")
```


## The App
The app enables the user to compare two models for the pressure in function of the temperature.
The models can be linear but also quadratic up to degree 4 (that is to say temperature^4). After choosing the type of model that will be fitted, the user should choose a value of temperature for which the pressure will be calculated.
And then, you just have to click on Submit.

The app can be found on [Shiny](https://amandineligot.shinyapps.io/DataProductAssignement) 

The ui.R and server.R files can be found on [Github](https://github.com/AmandineLigot/data-product-assignement.git) 



